Introduction

### 2024-04-12 Sections/Introduction.qmd
adding more citations to intro

Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012], anagram completion [@goodeSuperiorityVariableRepeated2008], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], task switching [@sabahWhenLessMore2019], associative learning [@leeEvidentialDiversityIncreases2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019], and training on a complex video game [@seowTransferEffectsVaried2019]. See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.

@@

The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning. Much of this research has been influenced by the work of (@schmidtSchemaTheoryDiscrete1975), who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced. Schema theory presumes that learners possess general motor programs for a class of movements (e.g. an underhand throw). When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task. Schema theory predicts that variable training facilitates the formation of more robust schemas, which will result in improved generalization or transfer. Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group. Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group. For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations. Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].

@@

Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; but see @stewartEffectCategoryVariability2002]. The results of @sakamotoPuttingPsychologyBack2008 are noteworthy. They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability. In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial. They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.

>>>>

Varied training has been shown to influence learning in wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021],  trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022]. See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.

@@

The influence of training variation has received a large amount of attention in the domain of sensorimotor skill learning. Much of this research has been influenced by the work of @schmidtSchemaTheoryDiscrete1975, who proposed a schema-based account of motor learning as an attempt to address the longstanding problem of how novel movements are produced. Schema theory presumes that learners possess general motor programs for a class of movements (e.g. an underhand throw). When called up for use motor programs are parameterized by schema rules which determine how the motor program is parameterized or scaled to the particular demands of the current task. Schema theory predicts that variable training facilitates the formation of more robust schemas, which will result in improved generalization or transfer. Experiments that test this hypothesis are often designed to compare the transfer performance of a constant-trained group against that of a varied-trained group. Both groups train on the same task, but the varied group practices with multiple instances along some task-relevant dimension that remains invariant for the constant group. For example, studies using a projectile throwing task might assign participants to either constant training that practicing throwing from a single location, and a varied group that throws from multiple locations. Following training, both groups are then tested from novel throwing locations [@pigottMotorSchemaStructure1984; @willeyLimitedGeneralizationVaried2018; @pachecoLearningSpecificIndividual2018; @wulfEffectTypePractice1991].

@@

Further observations consonant with the results of @cohenCategoryVariabilityExemplar2001  have since been observed in numerous investigations [@hahnEffectsCategoryDiversity2005; @perlmanFurtherAttemptsClarify2012;
@sakamotoPuttingPsychologyBack2008; @hsuEffectsGenerativeDiscriminative2010; but see @stewartEffectCategoryVariability2002 and @yangCategoryVariabilityEffect2014]. The results of @sakamotoPuttingPsychologyBack2008 are noteworthy. They first reproduced the basic finding of participants being more likely to categorize an unknown middle stimulus into a training category with higher variability. In a second experiment, they held the variability between the two training categories constant and instead manipulated the training sequence, such that the examples of one category appeared in an ordered fashion, with very small changes from one example to the other (the stimuli were lines that varied only in length), whereas examples in the alternate category were shown in a random order and thus included larger jumps in the stimulus space from trial to trial. They found that the middle stimulus was more likely to be categorized into the category that had been learned with a random sequence, which was attributed to an increased perception of variability which resulted from the larger trial to trial discrepancies.
